qcircuit 2.5.3 Tutorial

### 2017-09-27 CO681-QuantumInformationProcessing/assignments/assignment_01.tex
Assignment completed
edits

Since $\ket{0}$ and $\ket{+}$ lie in $\R^2$, the optimal $\ket{\phi_0}$ and $\ket{\phi_1}$ lie in $\R^2$ so as to optimize the length of projection of $\ket{\phi_0}$ and $\ket{\phi_1}$ onto $\ket{0}$ and $\ket{+}$ respectively (ie $\ip{\phi_0}{0}$ and $\ip{\phi_1}{+}$).

@@

>>>>

Since $\ket{0}$ and $\ket{+}$ lie in $\R^2$, there exist optimal $\ket{\phi_0}$ and $\ket{\phi_1}$ in $\R^2$. This can be seen by observing that $\abs{\ip{0}{\phi_0}}$ and $\abs{\ip{+}{\phi_1}}$ are invariant multiplications of $\ket{\phi_a}$ by some $e^{i\theta_a}$. With a bit of work, one can convince themselves we can always rotate an optimal solution in the real plane.

@@

\begin{align*}
\ket{\Psi}^{12}\ket{\Psi}^{34} &= \frac{1}{2}(\ket{00}^{12} + \ket{11}^{12})(\ket{00}^{34} + \ket{11}^{34}) \\
&= \frac{1}{2}(\ket{00}^{12}\ket{00}^{34} + \ket{00}^{12}\ket{11}^{34} + \ket{11}^{12}\ket{00}^{34} + \ket{11}^12\ket{11}^{34})\\
&= \frac{1}{2}(\ket{00}^{23}\ket{00}^{14} + \ket{01}^{23}\ket{01}^{14} + \ket{10}^{23}\ket{10}^{34} + \ket{11}^{23}\ket{11}^{34}).
\end{align*}
Choose $\ket{\phi_{ab}} = \ket{\Psi_{ab}}$ for $a,b \in \{0,1\}$. Observe that 
\begin{align*}
&\ \ \ \ket{\Psi_{00}}^{23}\ket{\Psi_{00}}^{14} + \ket{\Psi_{11}}^{23}\ket{\Psi_{11}}^{14} \\
&= \frac{1}{2}(\ket{00}^{23}\ket{00}^{14} + \ket{00}^{23}\ket{11}^{14} + \ket{11}^{23}\ket{00}^{14} + \ket{11}^{23}\ket{11}^{14}) \\
&+ \frac{1}{2}(\ket{00}^{23}\ket{00}^{14} - \ket{00}^{23}\ket{11}^{14} - \ket{11}^{23}\ket{00}^{14} + \ket{11}^{23}\ket{11}^{14}) \\
&= \ket{00}^{23}\ket{00}^{14} + \ket{11}^{23}\ket{11}^{14}.
\end{align*}
and similarly by symmetry
$$\ket{\Psi_{01}}^{23}\ket{\Psi_{01}}^{14} + \ket{\Psi_{10}}^{23}\ket{\Psi_{10}}^{14} = \ket{01}^{23}\ket{01}^{14} + \ket{10}^{23}\ket{10}^{14} $$
So using the above observations we see that
\begin{align*}
&\ \ \ \frac{1}{2}(\ket{\Psi_{00}}^{23}\ket{\phi_{00}}^{14} + \ket{\Psi_{01}}^{23}\ket{\phi_{01}}^{14} + \ket{\Psi_{10}}^{23}\ket{\phi_{10}}^{14} \ket{\Psi_{11}}^{23}\ket{\phi_{11}}^{14}) \\
&= \frac{1}{2}(\ket{\Psi_{00}}^{23}\ket{\Psi_{00}}^{14} + \ket{\Psi_{01}}^{23}\ket{\Psi_{01}}^{14} + \ket{\Psi_{10}}^{23}\ket{\Psi_{10}}^{14} \ket{\Psi_{11}}^{23}\ket{\Psi_{11}}^{14}) \\
&= \frac{1}{2}(\ket{00}^{23}\ket{00}^{14} + \ket{01}^{23}\ket{01}^{14} + \ket{10}^{23}\ket{10}^{34} + \ket{11}^{23}\ket{11}^{34})
\end{align*}
as desired.
Performing a Bell measurement on qubits $2$ and $3$ yields state $\ket{\Psi_{ab}}$ with probability $\frac{1}{4}$ and qubits $1$ and $4$ are left in state $\ket{\Psi_{ab}}$ (for $a,b \in\{0,1\}$).
